### 2012-09-11 demo/taxize.Rmd
added IUCN example
Added IUCN example
example without propt (knitr..)

## A somewhat realistic workflow
### User's species list 
```{r}
splist <- c("annona cherimola", 'annona muricata', "quercus robur", 
						"shorea robusta", "pandanus patina", "oryza sativa", "durio zibethinus")
```

@@

>>>>

## A somewhat realistic workflow
### User's species list 
```{r}
splist <- c("annona cherimola", 'annona muricata', 
						"shorea robusta", "pandanus patina", "durio zibethinus")
```

@@

*********
# IUCN Red List
## Query the Red List API
```{r}
ia <- iucn_summary(c("Panthera uncia", "Lynx lynx"))
```

### Extract Status
```{r}
laply(ia, function(x) x$status)
```
